A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-27 article/index.Rmd
Acknowledgements
reorganized the technical stuff at the end
update of affiliation

---
title: A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe
runninghead: Schmid.
author:
- name: Clemens Schmid
  num: 1
address:
- num: 1
  org: Institute of Pre- and Protohistoric Archaeology, Kiel University, Kiel, Germany
corrauth: "Clemens Schmid, Institut für Ur- und Frühgeschichte, Christian-Albrechts-Universität, D - 24098 Kiel."
email: clemens@nevrome.de
abstract: "Petersilie."
keywords: Bronze Age, Burial Traditions, Cultural Evolution, Cultural Transmission
classoption:
  - Afour
  - times
bibliography: ../references.bib
bibliographystyle: apalike
output:
  rticles::sage_article:
    keep_tex: yes
    includes:
        in_header: preamble.tex
---

@@

>>>>

---
title: A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe
runninghead: Schmid.
author:
- name: Clemens Schmid
  num: 1
address:
- num: 1
  org: Römisch-Germanisches Zentralmuseum, Leibniz-Forschungsinstitut für Archäologie, Mainz, Germany
corrauth: Clemens Schmid, Römisch-Germanisches Zentralmuseum, Leibniz-Forschungsinstitut für Archäologie, D - 55116 Mainz.
email: clemens@nevrome.de
abstract: Petersilie.
keywords: Bronze Age, Burial Traditions, Cultural Evolution, Cultural Transmission
classoption:
  - Afour
  - times
bibliography: ../references.bib
bibliographystyle: apalike
output:
  rticles::sage_article:
    keep_tex: yes
    includes:
        in_header: preamble.tex
---

@@

```{r child = '06_Remarks.Rmd'}
```
